Thermodynamic Structure of the Solar Corona: Tomographic Reconstructions and MHD Modeling

### 2019-12-26 lloveras_2020_Albert.tex
unas sugerencias

{We define next a measure of the average relative difference between the tomographic and the synthetic FBE in each voxel, as}

\begin{equation}\label{R}
R_i \, \equiv \ (1/K) \, \sum_{k=1}^K \left| \, 1 - \FBE^{(k)}_{i,\rm syn}\,/\,\FBE^{(k)}_{i,\rm tom}\, \right| \,,
\end{equation}

so that the final product of DEMT is in the form of 3D maps of the electron density and mean temperature. These relationships {were} derived in detail in \citealt{frazin_2009} (see Appendix C).\\
\temp{Aclarar que consideramos Ne como $\sqrt{<\Ne ^2>}$.} {ALBERT: Yo creo que es mejor hablar de $\sqravgN$}

\temp{DEMT has been improved since the previously published work. We now perform hollow-tomography with the EUV images, (definir hollow-tom) and a 3D regularized of the solution was applyed to obtain smother and more reliable result at the edge of the tomographic grid.} \notebyalbert{NOTA de Albert: Explicá que hacés sin justificarte. Luego aclará como se hizo eso en trabajos previos, y cual es el impacto esperado. Puedo proveer un párrafo de ejemplo, pero creo que será mejor que vos escribas como te salga y yo luego edito. Algo muy importante para todo el paper: proponete escribir ``párrafos modulares". Es decir que, con las razonables limitaciones, puedan moverse de lugar, de orden, y sigan funcionando. No definiría hollow-tomography, es un término coloquial interno nuestro. Lo correcto es que al hablar de datos mucho más arribas expliques que los datos del disco no se utilizan, pero no le des un nombre a la tomografía.}

@@

{Note that, for any given field line, all quantities in these two expresions can be computed from the DEMT and AWSoM models through Equations (\ref{Fc})-(\ref{Er}). Once computed, the quantity $\phi_h$ can be calculated, which is the energy input flux required at the coronal base of each coronal field-line required to mantain a stable coronal structure.}

@@

{To study the variation of the DEMT results in different magnetic structures we traced $\sqravgN$ and $\Tm$ along the magnetic field lines of the AWSoM model.} For both rotations, all field lines that meet the criteria listed in Section \ref{trace} were selected. For each field line, the data points of electron density and electron mean temperature as a function of height were fitted to the Equations \ref{Nfit} and \ref{Tfit}.

@@

\begin{table}
\begin{tabular}{l r@{.}l@{\hskip 0.05in} r@{\hskip 0.01in} r@{.}l  r@{.}l@{\hskip 0.05in} r@{\hskip 0.01in} r@{.}l r@{.}l@{\hskip 0.05in} r@{\hskip 0.01in} r@{.}l }
% r@{.}l@{\hskip 0.05in} r@{\hskip 0.01in} r@{.}l@{\hskip 0.01in} l}
\hline
Type    & \multicolumn{5}{c}{$\med(\NCB)$}             & \multicolumn{5}{c}{$\med(\lN)$} & \multicolumn{5}{c}{$\med(\avgTe)$} \\
       & \multicolumn{5}{c}{$[10^8\,{\rm cm}^{-3}]$}  & \multicolumn{5}{c}{$[{\rm 10}^{-2}\,\mrsun]$} & \multicolumn{5}{c}{$[\MK]$} \\
\hline
0    & 1&26 &(\Mi&17&4\%)  &   7&3 &(\Pl&13&6\%) &   1&09 &(\Pl&24&7\%) \\
I    & 1&13 &(\Mi&14&1\%)  &   8&3 &(\Pl&18&1\%) &   1&29 &(\Pl&20&1\%) \\
II   & 0&97 &(\Mi&20&6\%)  &   8&9 &(\Pl&29&1\%) &   1&33 &(\Pl&16&5\%) \\
III  & 0&66 &(\Mi&16&2\%)  &   7&7 &(\Pl&11&4\%) &   0&98 &(\Pl&~6&1\%) \\
\hline          
\end{tabular}
\caption{Median value (indicated as ``Md'') of the statistical distribution of $\NCB$, $\lN$, and $\aTm$ for each coronal type of lines defined in Section \ref{trace}. For CR-2082 values are expressed in absolute terms, while for CR-2208 they are informed as a percentual variation relative to the CR-2082 value.}
\label{tabla_demt}
\end{table}

@@

\begin{table}
\begin{tabular}{l r@{.}l@{\hskip 0.05in} r@{\hskip 0.01in} r@{.}l  r@{.}l@{\hskip 0.05in} r@{\hskip 0.01in} r@{.}l r@{.}l@{\hskip 0.05in} r@{\hskip 0.01in} r@{.}l }
% r@{.}l@{\hskip 0.05in} r@{\hskip 0.01in} r@{.}l@{\hskip 0.01in} l}
\hline
Type    & \multicolumn{5}{c}{$\med(\NCB)$}             & \multicolumn{5}{c}{$\med(\lN)$} & \multicolumn{5}{c}{$\med(\avgTe)$} \\
       & \multicolumn{5}{c}{$[10^8\,{\rm cm}^{-3}]$}  & \multicolumn{5}{c}{$[{\rm 10}^{-2}\,\mrsun]$} & \multicolumn{5}{c}{$[\MK]$} \\
\hline
CR-2082\\
I  & 1&13 &(\Mi&11&9\%)  &   8&3 &(\Mi&~2&4\%) &   1&29 &(\Mi&10&8\%) \\
II  & 0&97 &(\Mi&22&5\%)  &   8&9 &(\Pl&~2&2\%) &   1&33 &(\Mi&~4&5\%) \\
III  & 0&66 &(\Mi&16&8\%)  &   7&7 &(\Mi&~9&1\%) &   0&98 &(\Mi&~9&2\%) \\
\hline          
CR-2208\\
I  & 0&97 &(\Pl&~9&3\%)  &   9&8 &(\Mi&~7&1\%) &   1&55 &(\Mi&14&2\%) \\
II  & 0&77 &(\Pl&11&7\%)  &  11&6 &(\Mi&17&2\%) &   1&55 &(\Mi&~9&7\%) \\
III  & 0&56 &(\Mi&~1&9\%)  &   8&6 &(\Mi&16&3\%) &   1&04 &(\Mi&~9&6\%) \\
\end{tabular}
\caption{Median value (indicated as ``Md'') of the statistical distribution of $\NCB$, $\lN$, and $\aTm$ for each coronal type of lines defined in Section \ref{trace}. DEMT values are expressed in absolute terms, while AWSoM results are informed as a percentual variation relative to the corresponding DEMT value.}
\label{tabla_comp}
\end{table}

>>>>

\albert{We define next a measure of the accuracy of the LDEM model to predict the tomographic FBEs in each voxel, as}

\begin{equation}\label{R}
R_i \, \equiv \ (1/K) \, \sum_{k=1}^K \left| \, 1 - \FBE^{(k)}_{i,\rm syn}\,/\,\FBE^{(k)}_{i,\rm tom}\, \right| \, ,
\end{equation}

\noindent
\albert{being the average relative difference between the tomographic and the synthetic FBEs. The final product} of DEMT is in the form of 3D maps of the electron density and mean temperature. These relationships {were} derived in detail in \citealt{frazin_2009} (see Appendix C).\\
\temp{Aclarar que consideramos Ne como $\sqrt{<\Ne ^2>}$.} {ALBERT: Yo creo que es mejor hablar de $\sqravgN$}
\temp{DEMT has been improved since the previously published work. We now perform hollow-tomography with the EUV images, (definir hollow-tom) and a 3D regularized of the solution was applyed to obtain smother and more reliable result at the edge of the tomographic grid.} \notebyalbert{NOTA de Albert: Explicá que hacés sin justificarte. Luego aclará como se hizo eso en trabajos previos, y cual es el impacto esperado. Puedo proveer un párrafo de ejemplo, pero creo que será mejor que vos escribas como te salga y yo luego edito. Algo muy importante para todo el paper: proponete escribir ``párrafos modulares". Es decir que, con las razonables limitaciones, puedan moverse de lugar, de orden, y sigan funcionando. No definiría hollow-tomography, es un término coloquial interno nuestro. Lo correcto es que al hablar de datos mucho más arribas expliques que los datos del disco no se utilizan, pero no le des un nombre a la tomografía.}

@@

Note that, for any given field line, all quantities in these two expresions can be computed from the DEMT and AWSoM models through Equations (\ref{Fc})-(\ref{Er}). Once computed, the quantity $\phi_h$ can be calculated, which is the energy input flux \albert{required at the coronal base of each coronal field-line to mantain a stable coronal structure.}

@@

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.495\textwidth]{figs/map_Ne_CR2208_DEMT-AIA_H1_L522_r3d_1025_Rsun.pdf}
\includegraphics[width=0.495\textwidth]{figs/map_Tm_CR2208_DEMT-AIA_H1_L522_r3d_1025_Rsun.pdf}
\includegraphics[width=0.495\textwidth]{figs/map_Ne_CR2208_DEMT-AIA_H1_L522_r3d_1065_Rsun.pdf}
\includegraphics[width=0.495\textwidth]{figs/map_Tm_CR2208_DEMT-AIA_H1_L522_r3d_1065_Rsun.pdf}
\includegraphics[width=0.495\textwidth]{figs/map_Ne_CR2208_DEMT-AIA_H1_L522_r3d_1105_Rsun.pdf}
\includegraphics[width=0.495\textwidth]{figs/map_Tm_CR2208_DEMT-AIA_H1_L522_r3d_1105_Rsun.pdf}
\caption{\albert{Carrington maps of the measure $R$ defined by Equation (\ref{R}), for CR2082 (left panels) and CR2208 (right panels), at heights $1.025$, $1.065$ and $1.105\,\mrsun$, from top to bottom}. \notebyalbert{Aquí deberían ir los seis mapas de $R$ correspondientes. Quizá los saquemos, pero a esta altura es importante que los veamos nosotros para evaluar la precisión de predicción de las reconstrucciones de los resultados LDEM en la zona abierta. Quizá terminemos haciendo el comentario adecuado y sacamos la Figura, o quizá la dejamos, pero veamos esa info aquí. Noten el cambio en NARANJA que hice en torno de la Ecuación (4) más adelante.}}
\label{carmaps_R_2082_2208}
\end{center}
\end{figure}
{To study the variation of the DEMT results in different magnetic structures we traced $\sqravgN$ and $\Tm$ along the magnetic field lines of the AWSoM model.} For both rotations, all field lines that meet the criteria listed in Section \ref{trace} were selected. For each field line, the data points of electron density and electron mean temperature as a function of height were fitted to the Equations \ref{Nfit} and \ref{Tfit}.

@@

\begin{table}
\begin{tabular}{l r@{.}l@{\hskip 0.05in} r@{\hskip 0.01in} r@{.}l  r@{.}l@{\hskip 0.05in} r@{\hskip 0.01in} r@{.}l r@{.}l@{\hskip 0.05in} r@{\hskip 0.01in} r@{.}l }
% r@{.}l@{\hskip 0.05in} r@{\hskip 0.01in} r@{.}l@{\hskip 0.01in} l}
\hline
Type    & \multicolumn{5}{c}{$\med(\NCB)$}             & \multicolumn{5}{c}{$\med(\lN)$} & \multicolumn{5}{c}{$\med(\avgTe)$} \\
       & \multicolumn{5}{c}{$[10^8\,{\rm cm}^{-3}]$}  & \multicolumn{5}{c}{$[{\rm 10}^{-2}\,\mrsun]$} & \multicolumn{5}{c}{$[\MK]$} \\
\hline
0    & 1&26 &(\Mi&17&4\%)  &   7&3 &(\Pl&13&6\%) &   1&09 &(\Pl&24&7\%) \\
I    & 1&13 &(\Mi&14&1\%)  &   8&3 &(\Pl&18&1\%) &   1&29 &(\Pl&20&1\%) \\
II   & 0&97 &(\Mi&20&6\%)  &   8&9 &(\Pl&29&1\%) &   1&33 &(\Pl&16&5\%) \\
III  & 0&66 &(\Mi&16&2\%)  &   7&7 &(\Pl&11&4\%) &   0&98 &(\Pl&~6&1\%) \\
\hline          
\end{tabular}
\caption{Median value (indicated as ``Md'') of the statistical distribution of $\NCB$, $\lN$, and $\aTm$ for each coronal type of lines defined in Section \ref{trace}. For CR-2082 values are expressed in absolute terms, while for CR-2208 they are informed as a percentual variation relative to the CR-2082 value. \albert{Propongo que para todas las cantidades absolutas informes siempre dos cifras significativas, y que todos los porcentajes los redondees a cero decimales (o sea, a veces una y a veces dos cifras significativas) y que no uses puntos para estos nunca. Doy dos ejemplos para no dejar dudas. Para $\NCB$ de Type-II: $1.0\,(-21\%)$. Para $\aTm$ de Type-III: $1.0\,(+6\%)$.}}
\label{tabla_demt}
\end{table}

@@

\begin{table}
\begin{tabular}{l r@{.}l@{\hskip 0.05in} r@{\hskip 0.01in} r@{.}l  r@{.}l@{\hskip 0.05in} r@{\hskip 0.01in} r@{.}l r@{.}l@{\hskip 0.05in} r@{\hskip 0.01in} r@{.}l }
% r@{.}l@{\hskip 0.05in} r@{\hskip 0.01in} r@{.}l@{\hskip 0.01in} l}
\hline
Type    & \multicolumn{5}{c}{$\med(\NCB)$}             & \multicolumn{5}{c}{$\med(\lN)$} & \multicolumn{5}{c}{$\med(\avgTe)$} \\
       & \multicolumn{5}{c}{$[10^8\,{\rm cm}^{-3}]$}  & \multicolumn{5}{c}{$[{\rm 10}^{-2}\,\mrsun]$} & \multicolumn{5}{c}{$[\MK]$} \\
\hline
CR-2082\\
I  & 1&13 &(\Mi&11&9\%)  &   8&3 &(\Mi&~2&4\%) &   1&29 &(\Mi&10&8\%) \\
II  & 0&97 &(\Mi&22&5\%)  &   8&9 &(\Pl&~2&2\%) &   1&33 &(\Mi&~4&5\%) \\
III  & 0&66 &(\Mi&16&8\%)  &   7&7 &(\Mi&~9&1\%) &   0&98 &(\Mi&~9&2\%) \\
\hline          
CR-2208\\
I  & 0&97 &(\Pl&~9&3\%)  &   9&8 &(\Mi&~7&1\%) &   1&55 &(\Mi&14&2\%) \\
II  & 0&77 &(\Pl&11&7\%)  &  11&6 &(\Mi&17&2\%) &   1&55 &(\Mi&~9&7\%) \\
III  & 0&56 &(\Mi&~1&9\%)  &   8&6 &(\Mi&16&3\%) &   1&04 &(\Mi&~9&6\%) \\
\end{tabular}
\caption{Median value (indicated as ``Md'') of the statistical distribution of $\NCB$, $\lN$, and $\aTm$ for each coronal type of lines defined in Section \ref{trace}. DEMT values are expressed in absolute terms, while AWSoM results are informed as a percentual variation relative to the corresponding DEMT value. \albert{Propongo que para todas las cantidades absolutas informes siempre dos cifras significativas, y que todos los porcentajes los redondees a cero decimales (o sea, a veces una y a veces dos cifras significativas) y que no uses puntos para estos nunca. Ejemplo para CR-2082 $\NCB$ de Type-II: $1.0\,(-23\%)$. Ejemplo para CR-2208 $\lambda_N$ de Type-II: $12.0\,(-17\%)$. Ejemplo para CR-2208 $\aTm$ de Type-II: $1.6\,(-10\%)$.}}
\label{tabla_comp}
\end{table}
